

Load and view data.
```{r}
# Now load the data and look at the first few rows
data(wine, package="rattle.data")
head(wine)
```

Exercise 1: Remove the first column from the data and scale
it using the scale() function

```{r}
wine1 <- wine[2:14]
wine2 <- scale(wine1)
```

Method 1: A plot of the total within-groups sums of squares against the 
number of clusters in a K-means solution can be helpful. A bend in the 
graph can suggest the appropriate number of clusters. 

```{r}
wssplot <- function(data, nc=15, seed=1234){
	            wss <- (nrow(data)-1)*sum(apply(data,2,var))
               	      for (i in 2:nc){
		                      set.seed(seed)
	                        wss[i] <- sum(kmeans(data, centers=i)$withinss)}
	                plot(1:nc, wss, type="b", xlab="Number of Clusters",
	                        ylab="Within groups sum of squares")
	   }

wssplot(wine2)
```

Exercise 2:
* How many clusters does this method suggest? 
Method 1 suggests 3 clusters, we know this because it is the area where the curve drops and cluster 4 and beyond the difference is not as great. 
* Why does this method work? What's the intuition behind it?
The intuition is that kgroups are grouped by minimum sum of squares. After three clusters the decrease drops off, thus 3 clusters should be our optimal number. 
* Look at the code for wssplot() and figure out how it works

Method 2: Use the NbClust library, which runs many experiments
and gives a distribution of potential number of clusters.

```{r}

library(NbClust)
set.seed(1234)
nc <- NbClust(wine2, min.nc=2, max.nc=15, method="kmeans")
barplot(table(nc$Best.n[1,]),
	          xlab="Numer of Clusters", ylab="Number of Criteria",
		            main="Number of Clusters Chosen by 26 Criteria")
```

Exercise 3: How many clusters does this method suggest?
This method suggests 3 clusters based on the bar plot, with 14 attributes.

Exercise 4: Once you've picked the number of clusters, run k-means 
using this number of clusters. Output the result of calling kmeans()
into a variable fit.km

```{r}
set.seed(1234)
fit.km <- kmeans(wine2, centers = 3, nstart=25)
fit.km$size
```

Exercise 5: using the table() function, show how the clusters in fit.km$clusters
compares to the actual wine types in wine$Type. Would you consider this a good
clustering?

```{r}
table(wine$Type, fit.km$cluster)
```

Yes this is a good cluster, only 6 wines were misplaced.

Exercise 6:
* Visualize these clusters using  function clusplot() from the cluster library
* Would you consider this a good clustering?

```{r}
library(cluster)
clusplot(wine, fit.km$cluster)
```

The cluster plot explains 57.38%. It could be a stronger clustering. 


